The Two-Foot Rule: A game theoretic analysis of the pickoff limit in Major League Baseball

### 2024-12-11 documentation/arxiv/arxiv.tex
standardize indentation in Results section

    \begin{figure}[b]
      \centering
      \includegraphics[width = 0.5\textwidth]{figures/leads_overall.png}
      \caption{The curves show the distribution of the lead distances at first base in feet. The red curve shows all leads from 2022, while the blue curves show the leads from 2023 under different levels of disengagements. The vertical lines represent the mean in each situation.}
      \label{fig:leads-overall}
    \end{figure}

@@

        \begin{figure}
          \label{fig:prob-pickoff-attempt}
          \centering
          \includegraphics[width = 0.5\textwidth]{figures/prob_pickoff_attempt.png}
          \caption{The y-axis shows the probability of a pickoff attempt based on the lead distance on the x-axis. The blue lines represent the number of prior disengagements in our 2023 data, and the red line compares that to data from 2022.}
        \end{figure}

@@

        \begin{figure}
          \label{fig:prob-pickoff-success}
          \centering
          \includegraphics[width = 0.5\textwidth]{figures/prob_pickoff_success.png}
          \caption{The y-axis shows the likelihood of success on a pickoff attempt based on the lead distance on the x-axis. The blue lines represent the skill level of the pitcher at picking off runners, which was calculated in our random effects model}
        \end{figure}

@@

        \begin{figure}
          \label{fig:prob-sb-success}
          \centering
          \includegraphics[width = 0.5\textwidth]{figures/prob_sb_success.png}
          \caption{The y-axis shows the likelihood of success on a stolen base attempt based on the lead distance on the x-axis. The blue lines represent the skill of the runner in our 2023 model, and the red line compares that to a median runner from our 2022 model.}
        \end{figure}

@@

        \begin{figure}
          \label{fig:random-effect-catcher}
          \centering
          \includegraphics[width = 0.5\textwidth]{figures/catcher_effect.png}
          \caption{The x-axis shows the catcher's arm strength in miles per hour, while the y-axis shows their skill at preventing stolen bases according to our random effects model. A lower y-value means a catcher is better at preventing stolen bases.}
        \end{figure}

@@

         \begin{figure}
          \label{fig:random-effect-runner}
          \centering
          \includegraphics[width = 0.5\textwidth]{figures/runner_effect.png}
          \caption{The x-axis shows the runner's sprint speed in feet per second, while the y-axis shows their skill at stealing bases according to our random effects model. A higher y-value means a runner is better at stealing bases.}
        \end{figure}

@@

        \begin{figure}
          \label{fig:finding-optimal-lead}
          \centering
          \includegraphics[width = 0.5\textwidth]{figures/finding_optimal_lead.png}
          \caption{The y-axis shows the run expectancy of each lead distance on the x-axis. The blue curves represent the number of prior disengagements in the plate appearance, and the vertical lines mark the lead that maximizes the run expectancy in each situation.}
        \end{figure}

@@

        \begin{table}
          \centering
          \begin{tabular}{c|ccc}
            Count & 0 Disengagements & 1 Disengagement & 2 Disengagements\\
            \hline
            \input{tables/lead_by_count.tex}
          \end{tabular}
          \caption{Based on the count in each row, each entry shows the optimal lead distance (in feet) for a runner on 1B depending on the number of disengagements}
          \label{tab:count}
        \end{table}

@@

        \begin{table}
          \centering
          \begin{tabular}{c|ccc}
             Outs & 0 Disengagements & 1 Disengagement & 2 Disengagements\\
            \hline
            \input{tables/lead_by_runners_outs.tex}
          \end{tabular}
          \caption{Based on the number of outs in each row, each entry shows the optimal lead distance (in feet) for a runner on 1B depending on the number of disengagements}
          \label{tab:runners-outs}
        \end{table}

@@

        \begin{table}
          \centering
          \begin{tabular}{cc|ccc}
            Battery Skill  & Runner Skill & 0 Disengagements & 1 Disengagements & 2 Disengagements\\
            \hline
            \input{tables/lead_by_players.tex}
          \end{tabular}
          \caption{Based on the skill of the battery (pitcher and catcher) and the skill of the runner in each row, each entry shows the optimal lead distance for a runner on first base depending on the number of disengagements}
          \label{tab:players}
        \end{table}

@@

        \begin{table}
          \centering
          \begin{tabular}{c|ccc}
            Disengagements & Average Actual Lead & Average Recommended Lead & Actual Exceeds Recommendation\\
            \hline
            \input{tables/actual_vs_rec_lead.tex}
          \end{tabular}
          \caption{Each entry shows the average lead at 1st base based on the number of disengagements prior to the pitch. The recommended leads in the final column are based on our single-agent model. The final column shows the percent of pitches where the actual lead exceeds our recommendation.}
          \label{tab:actual-vs-rec}
        \end{table}

@@

        \begin{table}
          \centering
          \begin{tabular}{c|ccc}
            Count & 0 Disengagements & 1 Disengagement & 2 Disengagements\\
            \hline
            \input{tables/count_two_agent.tex}
          \end{tabular}
          \caption{Based on the count in each row, each entry shows the optimal lead distance (in feet) for a runner on 1B depending on the number of disengagements for our two-agent model}
          \label{tab:count-twoagent}
        \end{table}

>>>>

      \begin{figure}
        \centering
        \includegraphics[width = 0.5\textwidth]{figures/leads_overall.png}
        \caption{
          \it The curves show the distribution of the lead distances at first base in feet. The red curve shows all leads from 2022, while the blue curves show the leads from 2023 under different levels of disengagements. The vertical lines represent the mean in each situation.
        }
        \label{fig:leads-overall}
      \end{figure}

@@

      \begin{figure}
        \centering
        \includegraphics[width = 0.5\textwidth]{figures/prob_pickoff_attempt.png}
        \caption{
          \it The y-axis shows the probability of a pickoff attempt based on the lead distance on the x-axis. The blue lines represent the number of prior disengagements in our 2023 data, and the red line compares that to data from 2022.
        }
        \label{fig:prob-pickoff-attempt}
      \end{figure}

@@

      \begin{figure}
        \centering
        \includegraphics[width = 0.5\textwidth]{figures/prob_pickoff_success.png}
        \caption{
          \it The y-axis shows the likelihood of success on a pickoff attempt based on the lead distance on the x-axis. The blue lines represent the skill level of the pitcher at picking off runners, which was calculated in our random effects model.
        }
        \label{fig:prob-pickoff-success}
      \end{figure}

@@

      \begin{figure}
        \centering
        \includegraphics[width = 0.5\textwidth]{figures/prob_sb_success.png}
        \caption{
          \it The y-axis shows the likelihood of success on a stolen base attempt based on the lead distance on the x-axis. The blue lines represent the skill of the runner in our 2023 model, and the red line compares that to a median runner from our 2022 model.
        }
        \label{fig:prob-sb-success}
      \end{figure}

@@

      \begin{figure}
        \centering
        \includegraphics[width = 0.5\textwidth]{figures/catcher_effect.png}
        \caption{
          \it The x-axis shows the catcher's arm strength in miles per hour, while the y-axis shows their skill at preventing stolen bases according to our random effects model. A lower y-value means a catcher is better at preventing stolen bases.
        }
        \label{fig:random-effect-catcher}
      \end{figure}

@@

      \begin{figure}
        \centering
        \includegraphics[width = 0.5\textwidth]{figures/runner_effect.png}
        \caption{
          \it The x-axis shows the runner's sprint speed in feet per second, while the y-axis shows their skill at stealing bases according to our random effects model. A higher y-value means a runner is better at stealing bases.
        }
        \label{fig:random-effect-runner}
      \end{figure}

@@

      \begin{figure}
        \centering
        \includegraphics[width = 0.5\textwidth]{figures/finding_optimal_lead.png}
        \caption{
          \it The y-axis shows the run expectancy of each lead distance on the x-axis. The blue curves represent the number of prior disengagements in the plate appearance, and the vertical lines mark the lead that maximizes the run expectancy in each situation.
        }
        \label{fig:finding-optimal-lead}
      \end{figure}

@@

      \begin{table}
        \centering
        \begin{tabular}{c|ccc}
          Count & 0 Disengagements & 1 Disengagement & 2 Disengagements\\
          \hline
          \input{tables/lead_by_count.tex}
        \end{tabular}
        \caption{
          \it Based on the count in each row, each entry shows the optimal lead distance (in feet) for a runner on 1B depending on the number of disengagements.
        }
        \label{tab:count}
      \end{table}

@@

      \begin{table}
        \centering
        \begin{tabular}{c|ccc}
           Outs & 0 Disengagements & 1 Disengagement & 2 Disengagements\\
          \hline
          \input{tables/lead_by_runners_outs.tex}
        \end{tabular}
        \caption{
          \it Based on the number of outs in each row, each entry shows the optimal lead distance (in feet) for a runner on 1B depending on the number of disengagements.
        }
        \label{tab:runners-outs}
      \end{table}

@@

      \begin{table}
        \centering
        \begin{tabular}{cc|ccc}
          Battery Skill  & Runner Skill & 0 Disengagements & 1 Disengagements & 2 Disengagements\\
          \hline
          \input{tables/lead_by_players.tex}
        \end{tabular}
        \caption{
          \it Based on the skill of the battery (pitcher and catcher) and the skill of the runner in each row, each entry shows the optimal lead distance for a runner on first base depending on the number of disengagements.
        }
        \label{tab:players}
      \end{table}

@@

      \begin{table}
        \centering
        \begin{tabular}{c|ccc}
          Disengagements & Average Actual Lead & Average Recommended Lead & Actual Exceeds Recommendation\\
          \hline
          \input{tables/actual_vs_rec_lead.tex}
        \end{tabular}
        \caption{
          \it Each entry shows the average lead at 1st base based on the number of disengagements prior to the pitch. The recommended leads in the final column are based on our single-agent model. The final column shows the percent of pitches where the actual lead exceeds our recommendation.
        }
        \label{tab:actual-vs-rec}
      \end{table}

@@

      \begin{table}
        \centering
        \begin{tabular}{c|ccc}
          Count & 0 Disengagements & 1 Disengagement & 2 Disengagements\\
          \hline
          \input{tables/count_two_agent.tex}
        \end{tabular}
        \caption{
          \it Based on the count in each row, each entry shows the optimal lead distance (in feet) for a runner on 1B depending on the number of disengagements for our two-agent model.
        }
        \label{tab:count-twoagent}
      \end{table}
